% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\usepackage[T1]{fontenc}
\usepackage{mathpazo}
\usepackage[scaled]{helvet}
\usepackage{courier}
\normalfont

\usepackage[usenames,dvipsnames]{color}
\definecolor{MyNameColor}{rgb}{0.18,0.31,0.31}
\begin{document}

\newcommand{\me}{Matthew P.~Bohnsack}
\newcommand{\position}{Linux HPC Expert}
\newcommand{\employer}{HPC place}
\newcommand{\via}{somewhere}

\signature{\me}                           % name for signature
\longindentation=0pt                      % needed to get closing flush left
\let\raggedleft\raggedright               % needed to get date flush left


\begin{letter}{}%Ms. Terri Roberts \\
%Senior Staff Recruiter \\
%XYZ Corporation \\
%Rt. 56 \\
%Anytown, New Jersey 05867}


\begin{flushleft}
\textbf{\Large\textcolor{MyNameColor}{{\fontfamily{phv}\selectfont \me}}}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 3203 Embudito Dr. NE --- Albuquerque, NM 87111 \\
\hfill 505-821-9214 (home) or 505-284-1661 (office) \\
\hfill \texttt{bohnsack@gmail.com}
\end{flushright}
\vfill % forces letterhead to top of page


\opening{To Whom It May Concern:}

\noindent I am writing to apply for the \position~position at \employer.  I
learned of the opportunity via \via.

\noindent I am seeking a challenging new position and am open to relocation.  I
have more than a decade of practical and proven technical experience with
multiple significant Linux HPC systems.  In addition, I will be finishing up a
Master's degree in Computer Engineering in September.  My r\'{e}sum\'{e}
outlines my experience and education in more detail.  I hope you will take the
time to review it.

\noindent After you have reviewed my credentials, I would appreciate the
opportunity for a personal interview.  I have complete flexibility as to the
time and place of such an interview.  Making initial contact and setting up
logistics will work best via email, but you may also feel free to call my
office phone any time during the work week from approximately 8:00 AM until 5:00
PM mountain time.  You may also call my home phone during the work week after
about 6:30 PM or any time on the weekend.  Thank you very much for considering
me for the position.

\closing{Sincerely yours,}


\encl{r\'{e}sum\'{e}}

\end{letter}


\end{document}






